---
name: Christopher
surname: Mainey
position: "Intelligence Analyst"
address: "Healthcare Evaluation Data (HED), Univesity Hospitals Birmingham NHS Foundation Trust"
phone: 07708791765
www: www.hed.nhs.uk, www.mainard.co.uk
email: "chris.mainey@uh.nhs.uk"
twitter: chrismainey
github: chrismainey
linkedin: chrismainey
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::hyndman
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE,  fig.width=7, fig.height= 5)
library(vitae)
library(rorcid)
```

I am an NHS Data Scientist/Statistician/Analyst in Health Informatics. I am a member of the Healthcare Evaluation Data (HED) team at University Hospitals Birmingham NHS Foundation Trust (UHB).  My work focuses on modelling National Health Service (NHS) data, primarily using the national Hospital Episode Statistics (HES). I work primarily in `R` and SQL Server, and have experience with various statistical modelling and machine learning techniques. I have recently subitted my PhD thesis, focused on modelling methods for NHS incident reporting data, at UCL.

I advise and train hospitals, commissioners, regulators and the private sector on using data to manage hospitals, monitor mortality, performance and quality.  I have a passion for using information effectively to influence policy and impact people’s health and improve their hospital care.  I am an experienced trainer, presenter and post-grad teacher. I have build and release several R package, and keen contributor to the NHS-R Community. I leads a local `R` usergroup at UHB, and run a programme of `R` trainig courses for HED.

# Key skills

```{r skillzcloud}
skillz<-c(rep("teaching", 7), rep("R",15), rep("SQL",10), rep("GLM", 8), rep("regression", 6), rep("work planning",4), rep("line management", 3), rep("report writing",4),rep("regression trees", 4), rep("GAM",8), rep("text mining", 4), rep("case-mix adjusmtent",4), rep("marketshare analysis", 3), rep("neural networks", 2), rep("machine learning", 10), rep("Rmarkdown", 6), rep("R package dev", 6), rep("git",8), rep("multi-level models", 10), rep("data visualisation", 5), rep("training", 6), "Stata", rep("SAS",3), rep("Data Analysis", 10), rep("Data linkage", 5), rep("Communication", 3), rep("community organisation", 4), rep("trouble shooting",7), rep("course development",4), rep("hospital data", 8), rep("HES",4),  rep("NRLS",), rep("overdispersion", 7), rep("SPC", 6), rep("cusum", 5), rep("standardised mortality", 8), rep("benchmarking", 4), rep("statistical analysis", 8), "Auditing", rep("indicator development", 8), rep("spotfire", 10), rep("python",4), rep("epidemiological analysis", 2), rep("critical appraisal",2), rep("hypothesis testing", 3), rep("smoothing methods",2), "time-series analysis", "system design", "dashboard building", "web development", "Shiny", "ggplot2", "caret", "wordclouds", "topic modelling", "LDA", "mgcv", "glmnet", "FunnelPlotR", "NHSRdatasets", "randomForest", "tidyverse", "databases", "DBI", "odbc", "tidytext", "quanteda", "keras", "multinom", "gam", "rpart", "xaringan", "blogdown", "bookdown", "vitae", "leaflet", "Hugo", "Travis-CI", "Codecov", "testthat", "devtools", "usethis", "RStudio", "lme4", "glmmTMB")

library(tidytext)
library(ggwordcloud)
library(dplyr)

my_df<- data.frame(doc=1,words=skillz, stringsAsFactors = FALSE)

dt<-my_df %>% 
  group_by(doc, words) %>%
  summarise(freq = n()*10)

ggplot(dt, aes(label=words, size=freq, col=freq))+
  geom_text_wordcloud_area(eccentricity = 0.65, area_corr = TRUE, area_corr_power =0.8, grid_margin = 1)+
  #scale_size_area(max_size = 30) +
  scale_radius(range=c(0,30), limits=c(0, NA))+
  scale_color_viridis_c()+
  theme_minimal()

```


# Education

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "PhD Apllied Statistics and Machine Learning", "2014-19", "UCL", "London, UK",
  "PgCert. Public Health", "2014-14", "University of Birmingham", "Birmingham, UK",
  "CIPD Certificate in Training Practise", "2009", "CIPD/City College Coventry", "Coventry, UK",
  "BSc Microbiology with Industrial Experience", "2002-06", "University of Manchester", "Manchester, UK"
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```

# Employment History

```{r orcid1}

a<- rorcid::orcid_employments("0000-0002-3018-6171")$`0000-0002-3018-6171`$`affiliation-group`$summaries

orcid_data <- as.data.frame(unlist(a, recursive = TRUE))
orcid_data <- data.table::rbindlist(a, fill=TRUE)

orcid_data %>%
  detailed_entries(
    where = `employment-summary.organization.name`,
    what = `employment-summary.role-title`,
    when = glue::glue("{`employment-summary.start-date.year.value`} - {`employment-summary.end-date.year.value`}")
    
  )
```

# Selected Talks, presentations, and teaching experience

```{r}
tribble(
  ~ Type, ~ Year, ~ Where, ~ Desc,
  "Talk", 2019, "Enterprise Applications of the R Language (EARL)", "Implementing R use in an NHS Informatics service",
  "Talk", 2019, "Royal Statistical Society Conference", "CUSUMs and Funnel Plots for reporting standardised mortality",
  "Course", 2019, "NHS Gloucestershire", "Introduction to R: data manipulation, visualisation, and statistical analysis",
  "Talk", 2019, "The Health Foundation", "Statistical and Machine Learning methods for NHS Incident data",
  "Talk", 2018, "UCL PCPH Methodology Meeting","Dealing with noisy count data: strategies for tackling over-dispersion, using R",
  "Workshop", 2018, "UHB Internal", "Introduction to Statistical Process Control",
  "Workshop", 2018, "UHB Internal", "Introduction to Statistics",
  "Lecture", 2014 - 2018, "Various NHS Trusts", "Standaridsed Mortality Ratios",
  "Seminars", 2016-2018, "UCL Medical School", "Use of Evidence (MBChMB)",
  "Seminars", 2016-2018, "UCL Farr Institute", "Statistical Methods (MSc Data Science for Health)",
  
) %>% 
   detailed_entries(
    Desc,
    Type,
    Year, 
    Where
  )
```

# Publications

# Software

```{r orcid2}

tribble(
  ~ Package, ~ Summary, ~ Year,
  "FunnelPlotR", "Funnel Plots for Indirectly Standardised Ratios with overdispersion adjustment", "2019", 
  "NHSRdatasets", "NHS and Healthcare Related Data for Education and Training", "2019"
) %>% 
  brief_entries(Summary, Package, Year)
    

```


